---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hddmRstan

<!-- badges: start -->
<!-- badges: end -->

The goal of hddmRstan is to provide a convenient way to fit hierarchical drift diffusion models (DDM) using Rstan. Additionally, each of the DDM parameters can be linearly dependent on some variables.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("wjoycezhao/hddmRstan")
```

```{r step0, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
static_help <- function(pkg, topic, out, links = tools::findHTMLlinks()) {
  pkgRdDB = tools:::fetchRdDB(file.path(find.package(pkg), 'help', pkg))
  force(links)
  tools::Rd2HTML(pkgRdDB[[topic]], out, package = pkg,
                 Links = links, no_links = is.null(links))
}

static_help <- function(pkg, topic, out, links = tools::findHTMLlinks()) {
  pkgRdDB = tools:::fetchRdDB(file.path(find.package(pkg), 'help', pkg))
  force(links)
  tools::Rd2HTML(pkgRdDB[[topic]], out, package = pkg,
                 Links = links, no_links = is.null(links))
}
```
Load package
--------

```{r setup}
require(hddmRstan)
```





Format data
--------

* **subj_idx**: subject IDs; start from 1 and be consecutive.
* **response**: binary, 1 (upper boundary) or 0 (lower boundary).
* **rt**: response time in seconds.
* **other columns**: variables that DDM parameters are linearly dependent on.
```{r data}
unique(data_example$subj_idx) 
head(data_example)
```

Scale data when possible:
```{r data1}
data_example$trialNum = data_example$trialNum/200
head(data_example)
```



Run model
--------
```{r model1, echo=TRUE,message=FALSE}
test = 1
if(test){
  seed = 1
  warmup = 0
  iter = 10
  chains = 2
} else {
  seed = 1
  warmup = 500
  iter = 1000
  chains = 4
}

stan_data_hddm = runModel(
  data = data_example,
  #### or read from a .csv file
  ## file_name = 'data_sample.csv', 
  a_coef = 'Intercept',
  t_coef = 'Intercept',
  z_coef = c('Intercept', 'trialNum'),
  v_coef = c('Intercept', 'gain', 'loss'),
  seed = seed,
  warmup = warmup,
  iter = iter,
  refresh = iter/10,
  chains = chains,
  csv_name_para = NULL,
  csv_name_diag = NULL
)


```

Details about the runModel function
--------

```{r helpmodel1, eval = FALSE}
?runModel
```

```{r helpmodel2, echo = FALSE, results = "asis"}
tmp <- tempfile()
static_help("hddmRstan", "runModel", tmp)
out <- readLines(tmp)
headfoot <- grep("body", out)
cat(out[(headfoot[1] + 1):(headfoot[2] - 1)], sep = "\n")
```
Results
--------

To get the stanfit object, use the following 

```{r model2, show = T, dpi=300, fig.height = 24,, fig.width = 15, fig.align = "center", out.width = "96%", eval = FALSE}
stan_data_hddm$stan_hddm
```

Show model diagnostics
```{r model3, show = T, dpi=300, fig.height = 24,, fig.width = 15, fig.align = "center", out.width = "96%", echo = TRUE}
stan_data_hddm$diag
```

Show posteror distribution summary 

```{r model4, show = T, dpi=300, fig.height = 24,, fig.width = 15, fig.align = "center", out.width = "96%", echo = TRUE}
stan_data_hddm$para[,c(1:3,13)]
```
